### 2022-03-08 manuscript.tex
svg [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/b29421e075710adb5fe500990928b63a6ce51d6f.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/b29421e075710adb5fe500990928b63a6ce51d6f/checks
https://github.com/scherzerthesis/thesis/actions/runs/1952291727

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/ba19792e36f35c9e79fcd36a9f38341b8b47ea95/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/ba19792e36f35c9e79fcd36a9f38341b8b47ea95}{scherzerthesis/thesis@ba19792}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/b29421e075710adb5fe500990928b63a6ce51d6f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/b29421e075710adb5fe500990928b63a6ce51d6f}{scherzerthesis/thesis@b29421e}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}
